\begin{rightcolumn}
    %---------------------------------------------------------------------------------------
    %	TITLE  HEADER
    %----------------------------------------------------------------------------------------
    \fcolorbox{white}{accentcol}{\begin{minipage}[c][3.5cm][c]{1\mpwidth}
        \begin {center}
            \HUGE{ \textbf{ \textcolor{white}{ \uppercase{ João Roque Costa } } } } \\[-24pt]
            \textcolor{white}{ \rule{0.1\textwidth}{1.25pt} } \\[4pt]
            \large{ \textcolor{white} {Coimbra, Portugal} }
        \end {center}
    \end{minipage}} \\[14pt]
    \vspace{-12pt}
    
    %---------------------------------------------------------------------------------------
    %	PROFILE
    %----------------------------------------------------------------------------------------
    \vfill\null
    
%    \cvtext{
%    A Master's student in Computer Science at IST with a strong interest in \textbf{problem-solving}, \textbf{financial markets}, \textbf{artificial intelligence}, and \textbf{data science}.\\ \\
%    Eager to join a dynamic team, enhance my skills, and tackle new challenges in the IT industry. \\ \\
%    }

    %---------------------------------------------------------------------------------------
    %	WORK EXPERIENCE
    %----------------------------------------------------------------------------------------
    \vfill\null
    \cvsection{WORK EXPERIENCE}

    \cvevent
        {Oct 24 - Jan 25}
        {Teaching Assistant – Data Science}
        {Instituto Superior Técnico}
        {Invited to work as a Teaching Assistant for the \textbf{Data Science} course, where I was responsible for guiding students through practical lab sessions.}
        {}
        {}
        {}
    
    \vfill\null
    \cvevent
        {July 2018}
        {Software Development Intern}
        {\href{https://mariaadelaide.com/}{Maria Adelaide} and \href{http://playsketch.net}{Playsketch}}
        {Key contributions:{\cvlist{
            \item Developed and optimized the \textbf{email automation system}, improving workflow efficiency.
            \item After completing my work on the email automation system, I was awarded a \textbf{game development course}, where I built a \textbf{Space Invaders} clone and a \textbf{Number Wizard} game for mobile devices.
        }}}
        {}
        {}
        {}

   %---------------------------------------------------------------------------------------
   %	EDUCATION
   %----------------------------------------------------------------------------------------
   \vfill\null
   \cvsection{EDUCATION}


    \cvevent
        {Sep 23 - NOW}
        {M. Sc. Computer Science and Engineering}
        {Instituto Superior Técnico}
        {
        A two-year program where I chose to focus in:
        {\cvlist{
            \item \textbf{Machine Learning}: Deep Learning, Agent Learning, Multi-Agent Systems, Intelligent Decision Making
            \item \textbf{Data Science}: Data Visualization, Data Analysis, Data Integration
            \item \textbf{Cloud Computing}
            \item \textbf{Information Systems}
        }}
        I am currently writing my thesis on \textbf{Dimensionality Reduction on Disjoint Manifolds}. To complement my research, I enrolled in the \textbf{Optimization and Algorithms} course as an elective within my curriculum. Additionally, I plan to apply for publication with the \textbf{Association for the Advancement of Artificial Intelligence (AAAI)}.
        }
        {}
        {\cvlist{
            \item \textbf{Machine Learning and Data Science}: Sklearn, pandas, numpy;
            \item \textbf{Cloud Computing}: AWS;
            \item \textbf{Information Systems}: CmapTools, SQL Server Management Studio, \\Pentaho.
        }}
        {}

    \vfill\null
    \cvevent
        {Sep 20 – Jul 23}
        {B. Sc. in Computer Science and Engineering}
        {Instituto Superior Técnico}
        {Throughout my bachelor's degree, I worked on various projects that strengthened both my technical expertise and teamwork skills. Key areas of study and practical experience include:}
        {\cvlist{
            \item \textbf{Mathematics and Foundations}: \textbf{Differential and Integral Calculus}, \textbf{Physics}, \textbf{Linear Algebra}, \textbf{Discrete Mathematics}, \textbf{Probability and Statistics}, which later proved useful in my thesis research.
            \item \textbf{Low-Level Computing}: \textbf{Compilers}, \textbf{Operating Systems}, \textbf{Distributed Systems}, \textbf{Computer Architecture}, and \textbf{Computer Networks}, providing a solid understanding of system architecture and performance.
            \item \textbf{Data Science and Artificial Intelligence}: \textbf{Artificial Intelligence}, \textbf{Databases}, and \textbf{Machine Learning}, which sparked my interest and led me to further specialize in this area during my master's degree.
            \item \textbf{Management}: Developed foundational knowledge of company economics through the \textbf{Management} course.
        }}
        {\cvlist{
            \item \textbf{Database Management}: SQL for data storage and querying.
            \item \textbf{Systems Modeling}: \textbf{ArchiMate}, \textbf{Camunda Modeler}, and \textbf{Enterprise Architect (Sparx)}.
            \item \textbf{Programming}: \textbf{JavaScript} for human-computer interaction and computer graphics, \textbf{Python} (\textbf{NumPy, Pandas}) for machine learning, and \textbf{Java} for software development.
        }}
        {\cvlist{
            \item \textbf{Project Management and Teamwork}: Learned to effectively distribute tasks, collaborate on complex projects, and develop persistence in problem-solving.
        }}

    % hotfixes to create fake-space to ensure the whole height is used
    \mbox{}
    \vfill
    \mbox{}
    \vfill
    \mbox{}
    \vfill
    \mbox{}
    \end{rightcolumn}
    